Type Refinements for the Working Class

### 2015-11-22 paper.tex
Define parametric refinement (#7)

Fixing a signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ in the abt
framework, we will define the notion of behavioral refinement by propounding
several judgments and their semantical explanations.

@@

>>>>

Fixing a signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ in the abt
framework, we will define the notion of behavioral refinement by propounding
several judgments and their semantical explanations. Let us first define the
presheaf of $\tau$-sorted expressions, $\Exprs_\tau$ as follows
\[
  \Define{
    \Exprs_\tau(\Upsilon\parallel\Gamma)
  }{
    \MkSet{M \mid \IsAbtUnmoded{\cdot}{\Upsilon}{\Gamma}{M}{\tau}}
  }
\]

We will also write $\Exprs_\tau$ for the presheaf $\Exprs_\tau(-\parallel\cdot)$ on $\SCtx$.

@@

The first judgment that will concern us is called \emph{parametric refinement},
$\Refines{\Upsilon}{\phi}{\tau}$, which means that $\phi$ refines the sort
$\tau$ under the symbolic parameters $\Upsilon$. We define this judgment
through a meaning explanation in the style of Martin-L\"of as follows:

\newcommand\RefEquate[4]{#1\{\IMode{#2}\}\left(\IMode{#3},\IMode{#4}\right)}

\begin{definition}
  To know $\Refines{\Upsilon}{\phi}{\tau}$ (presupposing $\IsSymCtx{\Upsilon}$
  and $\IsSort{\tau}$) is to know, for any $\Of{\rho}{\Upsilon\inj\Upsilon'}$,
  what it means for any $\Member{M,N}{\Exprs_\tau(\Upsilon')}$ to be equated by
  $\phi$ (written $\RefEquate{\phi}{\rho}{M}{N}$), such that
  $\RefEquate{\phi}{\rho}{\cdot}{\cdot}$ is a partial equivalence relation on
  $\Exprs_\tau(\Upsilon')$. Morever, that for any
  $\Of{\rho'}{\Upsilon'\inj\Upsilon''}$, from $\RefEquate{\phi}{\rho}{M}{N}$ we
  may conclude $\RefEquate{\phi}{\rho'\circ\rho}{M\rho'}{N\rho'}$.
\end{definition}
